Natural Stories LM analysis

### 2020-07-20 Analysis/nat_stories_gam.Rmd
new gams

## GAMs

Using only pre-error data.

Does not have hierarchical effects.

@@

```{r gams-2}
gam_ngram_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=ngram_data, method="REML")

>>>>

### GAMs

## Try 1
Using only pre-error data.

Does not have hierarchical effects. Has smooths for the surprisals, and tensor effects/interactions for the freq x length

@@

```{r gams}
gam_ngram_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=ngram_data, method="REML")

### 2020-07-20 Analysis/nat_stories_lms.Rmd
new gams

We sometimes center the predictors, but don't rescale them. (We center them for the brm models, but don't center surprisal for the GAM model).

@@

ggplot(select_labs, aes(length))+geom_bar()

@@

## GAMs

I think there might be ways to have mixed effects for this, but for now we're not. Also, couldn't figure out good ways of getting graphs from the full models, so just fitting the pieces within ggplot for graphs.

Using only pre-error data.

```{r gams-2}
gam_ngram_1 <- gam(rt ~ s(ngram_surp, bs="cr", k=20)+ te(freq, length, bs="cr")+s(past_ngram, bs="cr", k=20)+te(past_freq, past_length, bs="cr"), data=labelled_pre_error)

gam_txl_1 <- gam(rt ~ s(txl_surp, bs="cr", k=20)+ te(freq, length, bs="cr")+s(past_txl, bs="cr", k=20)+te(past_freq, past_length, bs="cr"), data=labelled_pre_error)

gam_grnn_1 <- gam(rt ~ s(grnn_surp, bs="cr", k=20)+ te(freq, length, bs="cr")+s(past_grnn, bs="cr", k=20)+te(past_freq, past_length, bs="cr"), data=labelled_pre_error)

```{r}
for_graph <- labelled_pre_error %>% 
  select(rt, txl_surp, ngram_surp, grnn_surp, past_txl, past_grnn, past_ngram) %>%
  pivot_longer(cols=`txl_surp`:`past_ngram`,names_to="label", values_to="data") %>% 
  mutate(type=case_when(
         label %in% c("past_ngram", "past_txl", "past_grnn")~"Previous",
         T~"Current"),
         model=case_when(
           label %in% c("txl_surp", "past_txl")~"TXL",
           label %in% c("grnn_surp", "past_grnn")~"GRNN",
           T ~ "5-gram"
         ))

ggplot(for_graph, aes(x=data, y=rt))+
         geom_smooth(method="gam",formula= y~s(x, bs="cr", k=20),color="black")+
         facet_grid(type~model)+
        labs(x="Surprisal (bits)", y="Reaction Time (ms)")

ggsave("../Papers/gam.pdf", width=3.5, height=2, unit="in")

Including post-error data.

```{r gams-3}
gam_ngram_2 <- gam(rt ~ s(ngram_surp, bs="cr", k=20)+ te(freq, length, bs="cr")+s(past_ngram, bs="cr", k=20)+te(past_freq, past_length, bs="cr"), data=labelled_post_error)

gam_txl_2 <- gam(rt ~ s(txl_surp, bs="cr", k=20)+ te(freq, length, bs="cr")+s(past_txl, bs="cr", k=20)+te(past_freq, past_length, bs="cr"), data=labelled_post_error)

gam_grnn_2 <- gam(rt ~ s(grnn_surp, bs="cr", k=20)+ te(freq, length, bs="cr")+s(past_grnn, bs="cr", k=20)+te(past_freq, past_length, bs="cr"), data=labelled_post_error)

```{r plot_gam-3}
for_graph_2 <- labelled_post_error %>% 
  select(rt, txl_surp, ngram_surp, grnn_surp, past_txl, past_grnn, past_ngram) %>%
  pivot_longer(cols=`txl_surp`:`past_ngram`,names_to="label", values_to="data") %>% 
  mutate(type=case_when(
         label %in% c("past_ngram", "past_txl", "past_grnn")~"Previous",
         T~"Current"),
         model=case_when(
           label %in% c("txl_surp", "past_txl")~"TXL",
           label %in% c("grnn_surp", "past_grnn")~"GRNN",
           T ~ "5-gram"
         ))

ggplot(for_graph_2, aes(x=data, y=rt))+
         geom_smooth(method="gam",formula= y~s(x, bs="cr", k=20),color="black")+
         facet_grid(type~model)+
        labs(x="Surprisal (bits)", y="Reaction Time (ms)")

# TODOs for future

In terms of surprisal analyses, the possible next steps are doing GAM analysis more robustly (with mixed effects, presenting results from the models) and doing DTSR.

We could also try looking at the specific syntactic features that are in the dataset (the point of natural stories was to have a bunch of idioms and weird syntax); we could maybe analyse those?

>>>>

We center the predictors for the brms models, but don't rescale them.

@@

lab_summary
```

@@

## Log likelihoods

```{r}
# a <- log_lik(brm_ngram_interact)
# 
# a2 <- add_criterion(brm_ngram_interact, "waic")
# 
# b <- log_lik(brm_grnn_interact)
# 
# c <- log_lik(brm_txl_interact)
```
